---
title: "Credit Card defaulters Analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    #runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
library(DT)
library(rpivotTable)
library(ggplot2)
library(plotly)
library(dplyr)
library(openintro)
library(ggvis)
library(reshape2)
library(unbalanced)  
library(rpart)       
library(randomForest)
library(e1071)  
library(nnet) 
library(caret)  
library(pROC)   
library(stringi)
library(ggthemes)
library(ggcorrplot)
library(xgboost)
library(Matrix)
library(XLConnect)
library(DT)
```

```{r global, include=FALSE}
data <- read.csv("details1.csv")
ref_data <- data
colnames(data)[colnames(data)=="default.payment.next.month"] <- "default_payment"
dupdata <- data
data[, 1:25] <- sapply(data[, 1:25], as.character)
data[, 1:25] <- sapply(data[, 1:25], as.numeric)

data$EDUCATION[data$EDUCATION == 0] <- 4
data$EDUCATION[data$EDUCATION == 5] <- 4
data$EDUCATION[data$EDUCATION == 6] <- 4
data$MARRIAGE[data$MARRIAGE == 0] <- 3

#for data exlporation
dupdata$EDUCATION[dupdata$EDUCATION == 0] <- 4
dupdata$EDUCATION[dupdata$EDUCATION == 5] <- 4
dupdata$EDUCATION[dupdata$EDUCATION == 6] <- 4
dupdata$MARRIAGE[dupdata$MARRIAGE == 0] <- 3
dupdata$AGE <-cut(dupdata$AGE, breaks = c( 10, 30,50,100), labels = c("young", "middle","senior"))
dupdata$SEX<-cut(dupdata$SEX, 2,labels = c("Female","Male"))
dupdata$MARRIAGE<-cut(dupdata$MARRIAGE, 4,labels = c("married","single","Divorced","other"))
dupdata$EDUCATION<-cut(dupdata$EDUCATION, 4,labels = c("GraduateSchool","University","High school","Other"))

set.seed(123)
correlationMatrix <- round(cor(data),1)
highlyCorrelated <- findCorrelation(correlationMatrix, cutoff=0.8,verbose=T)
data <- data[,-highlyCorrelated]
dupdata <- dupdata[,-highlyCorrelated]
data <- data[,-c(1,6)]
dupdata <- dupdata[,-c(1)]

data1 <- data
data1[, c(1,5:17)] <- scale(data1[, c(1,5:17)])

data1[,c(2:4,18)] <- data.frame(apply(data1[c(2:4,18)],2, as.factor))
#str(data1)
ind <- sample(2,nrow(data1),replace = T,prob = c(0.8,0.2))
train <- data1[ind==1,]
test <- data1[ind==2,]

train1 <- sparse.model.matrix(default_payment~.-1,data = train)
train_label <- train[,"default_payment"]
train_matrix <- xgb.DMatrix(data = as.matrix(train1), label = train_label)

test1 <- sparse.model.matrix(default_payment~.-1,data = test)
test_label <- test[,"default_payment"]
test_matrix <- xgb.DMatrix(data = as.matrix(test1), label = test_label)


# Parameters
nc <- as.numeric(as.character(length(unique(train_label))))
xgb_params <- list("objective" = "binary:logistic",
                   "eval_metric" = "mlogloss",
                   "num_class" = nc)
watchlist <- list(train = train_matrix, test = test_matrix)

# eXtreme Gradient Boosting Model
#bst_model <- xgb.train(params = xgb_params,
 #                      data = train_matrix,
  #                     nrounds = 100,
   #                    watchlist = watchlist)

source("logistic.R")
source("random_forest_model.R")

results <- merge(logistic_results, rf_results, by='id')
```

EDA
======================================


Row
----------------------------


### Density Plot for Gender

```{r}
p2 <- ggplot(dupdata, aes(x = SEX, fill = default_payment)) + geom_density()+ xlab("Gender") + ylab("Default Payment Status") 

ggplotly(p2)
```


### Gender wise Distribution


```{r}
p <- ggplot(data=dupdata, mapping = aes(x=SEX, fill=default_payment)) + geom_bar()+ xlab("Gender") + ylab("Customer Counts") +theme_few()

ggplotly(p)
```

Row
----------------------------

### Age wise Density Plot

```{r}
p3 <- ggplot(dupdata, aes(x = AGE, fill = default_payment)) + geom_density()+ xlab("Age Category") + ylab("Customer Counts") 

ggplotly(p3)
```

### Age wise boxplot

```{r}
p <- ggplot(data=dupdata,mapping = aes(x=AGE,y=dupdata$LIMIT_BAL,fill=default_payment)) + geom_boxplot()+ xlab("Age Category") + ylab("Bank Balance")  

ggplotly(p)
```

Row
----------------------------

### Education 

```{r}
p4 <-  ggplot(data=dupdata,mapping = aes(x=EDUCATION,y=dupdata$LIMIT_BAL,fill=default_payment)) + geom_boxplot()+ xlab("Education") + ylab("Bank Balance")  

ggplotly(p4)
```

### Heat Map for Education - Age

```{r}
dupdata %>% group_by(EDUCATION,AGE) %>% summarise(mn_creditlmt=mean(LIMIT_BAL)) -> df
p5 <- ggplot(df, aes(EDUCATION, AGE, fill=mn_creditlmt)) + geom_tile() + scale_fill_gradient(low="white", high="steelblue")

ggplotly(p5)
```

Row
-----------------------

### Marital Status wise Distribution

```{r}
p <- ggplot(data=dupdata, mapping = aes(x=MARRIAGE, fill=default_payment)) + geom_bar()+ xlab("Marital Status") + ylab("Customer Counts")  +theme_few()

ggplotly(p)
```


Correlation Plot
=======================

### Correlation Plot

```{r}
pc <- ggcorrplot(correlationMatrix, hc.order = TRUE, type = "lower",outline.col = "white")+ theme(axis.text.x=element_text(angle=90, hjust=1))

#a <- melt(correlationMatrix)
#c <- a[a$Var2=='default_payment',]
#pc <- ggplot(a, aes(Var1, Var2, fill = value)) +geom_tile()+  scale_fill_gradient2(low="blue", mid="white", high="red") + theme(axis.text.x=element_text(angle=90, hjust=1))
#ggplotly(pc)
pc
```


LR Prediction Stats
============================================

### Confusion Matrix for Logistic Regression

```{r}
print(accuracy)
```

### Accuracy

```{r}
sum(diag(accuracy))/sum(accuracy)
```

Row
----------------------

### AUC Curve for Logistic Regression

```{r}
plot(roccurve)
```

Row
------------------------

### AUC value

```{r}
print(roccurve)
```

RF Prediction Stats
============================================

### Confusion Matrix for Random Forest

```{r}
print(cnf_rf)
```

Row
----------------------------


### AUC Curve for Random Forest

```{r}
plot(df_roc,main="AUC" %s+% df_roc$auc)
```


Summary {data-orientation=columns} 
===========================================


Column
---------------------------

Report

* The accuracy for Logistic Regression Model is `r sum(diag(accuracy))/sum(accuracy)`.

* The accuracy for Random Forest Model is `r accuracyrf`.



This report was generated on `r format(Sys.Date(), format = "%B %d, %Y")`.


Predicted Results
============================================

```{r}

datatable(results,
          caption = "Predicted Data",
          rownames = T,
          filter = "top",
          extensions = 'Buttons',
      options = list(
        pageLength = 50,
        dom = 'Blfrtip',
        buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
      ))

```


About Report
========================================

Created by: Vignesh EA

Confidential: Nothing like that!






